Analysis of NLA17 Dissolved Gas Indicator

### 2021-02-01 scripts/dgIndicatorAnalysis.Rmd
updated path to current data object

```{r}
# Read data file 
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-01-14.RData"))

>>>>

```{r}
# Read data file 
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-02-01.RData"))
